Supporting Information: The Transport Mechanisms of Polar Solutes in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-04-01 Ben_Manuscripts/transport/Supporting_Information.tex
Updated outline

  \subsection{Solute Interaction}\label{section:solute_interaction}

@@

  \subsection{Pore Splines}\label{section:splines}

@@

  \subsection{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}

@@

  \subsection{Solute Pairing with Sodium}

@@

  %BJC: could probably safely remove this figure
  \subsection{Mercaptoethanol's range of behavior}

@@

  \subsection{THF-sodium Complexation}

>>>>

  \section{Solute Interaction}\label{section:solute_interaction}

@@

%  \subsection{Sensitivity of Breakdown radius of Stokes-Einstein Equation}\label{section:se_sensitivity}
%  
%  In the main text, we estimated the trend in solute MSDs using the Stokes-Einstein
%  equation with the correction factor of Gierer and Wirtz, $f$, given by 
%  equation~\ref{M-eqn:correction_factor}. As $r \rightarrow \infty$ , $f \rightarrow 1$.
%  
%  We assumed that the Stokes-Einstein relationship could be approximated as a
%  piecewise function where the correction factor of Gierer and Wirtz, $f$, given
%  by equation~\ref{M-eqn:correction_factor} of the main text, is only applied below
%  a critical radius. At radii greater than the critical radius, $f$ = 1.
%  
%  In the main text, we constrained the corrected Stokes-Einstein equation so that
%  it passed through the highest MSD value. We also plotted the uncorrected 
%  Stokes-Einstein equation ($f$=1) as a lower bound to our expectations for 
%  unrestricted solute motion. The lower bound is relatively insensitive to our
%  choice of critical radius. Even for an unrealistically small critical radius 
%  of 0.5 nm, the curve is within
%  
%  \begin{figure}[!htb]
%  \centering
%  \includegraphics[width=0.45\textwidth]{stokes_intersection_sensitivity.pdf}
%  \caption{We varied the molecular radius at which we assumed the Stokes-Einstein
%  (SE) relationship to breaks down. It is assumed that the Gierer and Wirtz correction
%  to the SE equation becomes a more accurate estimation of MSD at small radii, after
%  the point of intersection }\label{fig:se_intersection_sensitivity}
%  \end{figure}

  \section{Solute MSD Ranking Time Lag Sensitivity}\label{section:lag_sensitivity}

  We chose to report the MSD of our solutes after a 400 ns time lag. This choice does
  not have a significant influence on the ranking of the solute MSDs. Although there
  is minor re-ranking among solutes with similar MSDs, it does not affect any of 
  the conclusions drawn in the main text.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_2.pdf}
  \caption{Time lag = 200 ns}\label{fig:F0.2}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_3.pdf}
  \caption{Time lag = 300 ns}\label{fig:F0.3}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_4.pdf}
  \caption{Time lag = 400 ns}\label{fig:F0.4}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_5.pdf}
  \caption{Time lag = 500 ns}\label{fig:F0.5}
  \end{subfigure}
  \begin{subfigure}{0.325\textwidth}
  \includegraphics[width=\textwidth]{all_10wt_tamsds_F0_6.pdf}
  \caption{Time lag = 600 ns}\label{fig:F0.6}
  \end{subfigure}
  \caption{The choice of time lag used to report solute MSDs does not 
  influence the trends reported in the main text. We observe minor re-ranking
  of solutes with similar MSDs and note that longer time lags generally
  lead to large error bars on the MSDs, as expected. }\label{fig:lag_sensitivity}
  \end{figure}

  \section{Pore Splines}\label{section:splines}

@@

  \section{Hydrogen Bond Detection Sensitivity}\label{section:hbond_sensitivity}

@@

  \section{Total Membrane Density}\label{section:total_density}

  In our simulations, we observe that water partitions into the tail region
  because of the tails' low density. We plotted the density of all atoms in 
  the system as function of their $xy$ positions within the unit cell. The 
  pore centers of the 5 and 10 wt \% water systems have a relatively low density
  that is comparable to the density in the tails far from the pore center
  (see figures~\ref{fig:total_density_5wt} and~\ref{fig:total_density_10wt}).
  The density is highest near the middle of the tails. The observed density distribution
  is necessary in order for the wedge-shaped monomers to fill space and stay in
  the hexagonal phase. Accordingly, water is densest in the pore center and at 
  the tail ends (see figures~\ref{fig:total_water_density_5wt} 
  and~\ref{fig:total_water_density_10wt}). Very little water is present in the 
  dense mid-tail region.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
  \end{subfigure}
  \caption{The lowest density regions of both membranes are in the pore center and in the
  tail region, furthest from the pore center (a \& c). Water is densest in the low density
  regions (b \& d).}\label{fig:total_density}
  \end{figure}

  \section{Solute Pairing with Sodium}

@@

  %BJC: could probably safely remove this figure
  \section{Mercaptoethanol's range of behavior}

@@

  \section{THF-sodium Complexation}
